Constraints on tensor and scalar couplings from $B\to K\bar\mu\mu$ and $B_s\to \bar\mu\mu$

### 2015-08-04 tensor/draft/draft-tensor-op.tex
[draft] Discuss comments in section 1 and 2

\thankstext[$\star$]{t1}{\christoph{Preprint: EOS-2015-03,} FLAVOUR(267104)-ERC-107}
\thankstext{e1}{e-mail: frederik.beaujean@lmu.de}
\thankstext{e2}{e-mail: christoph.bobeth@ph.tum.de}
\thankstext{e3}{e-mail: sjahn@mpp.mpg.de}

@@

\begin{abstract}
  The angular distribution of $B\to K\bar\ell\ell$ ($\ell = e,\,\mu,\,\tau$)
  depends on two parameters, the lepton forward-backward asymmetry, $A_{\rm
    FB}^\ell$, and the flat term, $F_H^\ell$. Both are strongly suppressed in
  the standard model and constitute sensitive probes of tensor and scalar
  contributions. We use the latest experimental results for $\ell = \mu$ in
  combination with \christoph{branching ratio of} $B_s\to \bar\mu\mu$ to derive the strongest model-independent
  bounds on tensor and scalar effective couplings to date. The measurement of
  $F_H^\mu$ \christoph{provides complementary constraints} to that of the branching ratio of $B_s\to
  \bar\mu\mu$ and allows us---for the first time---to constrain all
  complex-valued (pseudo-)scalar couplings and their chirality-flipped
  counterparts in one fit. Based on Bayesian fits of various scenarios, we find
  that our bounds even become tighter when vector couplings are allowed to
  deviate from the standard model and that specific combinations of angular
  observables in $B \to K^*$ are still allowed to be up to two orders of
  magnitude larger than in the standard model, which would place them in the
  region of LHCb's sensitivity.
\end{abstract}

@@

With the analysis of the data collected by the LHCb Collaboration
during \christoph{Run} I at the Large Hadron Collider (LHC), we now have access
to rather large samples of rare \christoph{$B$-meson} decays with branching ratios
below $10^{-5}$. As a consequence, angular analyses of three- and
four-body final states can be used to measure a larger number of
observables than previously possible at the B factories BaBar and
Belle. In this work we focus on rare $B$ decays driven at the parton
level by the flavor-changing neutral-current (FCNC) transition $b\to s
\bar\ell\ell$ that constitutes a valuable probe of the standard model
(SM) and provides constraints on its extensions.

@@

Both \christoph{angular} observables, $F_H^\ell$ and $A_{\rm FB}^\ell$, exhibit strong suppression
factors for vector and dipole couplings present in the SM, thereby enhancing
their sensitivity to tensor and scalar couplings \cite{Bobeth:2007dw,
  Bobeth:2012vn}. A similar enhancement of scalar couplings compared to
helicity-suppressed vector couplings of the SM is well-known from $B_s\to
\bar\mu\mu$. Unfortunately the limited data set of $B\to K^*(\to K\pi)
\bar\ell\ell$ from LHCb \cite{Aaij:2013qta} \christoph{did not yet} allow to perform a full
angular analysis without the assumption of vanishing scalar and tensor couplings
in this decay mode. In the future with more data or special-purpose analysis
techniques like the method of moments~\cite{beaujean:2015mom}, certain angular
observables in $B\to K^* \bar\ell\ell$ will provide additional constraints on
such couplings, as for example $J_{6c}$ \cite{Altmannshofer:2008dz} and the
linear combinations $(J_{1s} - 3 J_{2s})$ and $(J_{1c} + J_{2c})$
\cite{Matias:2012xw, Bobeth:2012vn} as well as the experimental test of the
relations $H_T^{(2)} = H_T^{(3)}$ and $J_7 = 0$~\cite{Bobeth:2012vn} at low
hadronic recoil.

@@

In the framework of the $|\Delta B| = |\Delta S| = 1$ effective theory
\begin{equation}
  \label{eq:Heff}
\begin{aligned}
  {\cal L}_{\rm eff}  =
   \frac{4 G_F}{\sqrt{2}} \,\frac{\alE}{4 \pi}\, & V_{tb}^{} V_{ts}^\ast
      \, \Big[ \christoph{C_7(\mu_b) \Op_7 + C_{7'}(\mu_b) \Op_{7'}}
 \\ & +
       \sum_{\ell = e,\, \mu,\, \tau} \sum_i  \wilson[\ell]{i}(\mu_b)
       \christoph{\Op_i^\ell} \Big] + \text{h.c.}
   \christoph{\,,}
\end{aligned}
\end{equation}
the most general dimension-six flavor-changing operators \christoph{$\Op_i^{(\ell)}$} mediating $b\to
s \gamma$ and $b\to s \bar\ell\ell$ are classified according to their chiral
structure. There are dipole ($i = 7,7'$) and vector ($i = 9,9',10,10'$) operators
\begin{equation}
  \label{eq:SM:ops}
\begin{aligned}
  \Op_{7(7')} &
  = \frac{m_b}{e}\!\[\bar{s} \sigma^{\mu\nu} P_{R(L)} b\] F_{\mu\nu}\,,
\\
  \christoph{\Op_{9(9')}^\ell} &
  = \[\bar{s} \gamma_\mu P_{L(R)} b\]\!\[\bar{\ell} \gamma^\mu \ell\]\,,
\\[0.1cm]
  \christoph{\Op_{10(10')}^\ell} &
  = \[\bar{s} \gamma_\mu P_{L(R)} b\]\!\[\bar{\ell} \gamma^\mu \gamma_5 \ell\]\,,
\end{aligned}
\end{equation}
further scalar ($i = S,S',P,P'$) operators
\begin{equation}
  \label{eq:scalar:ops}
\begin{aligned}
  \christoph{\Op_{S(S')}^\ell} &
  = \[\bar{s} P_{R(L)} b\]\!\[\bar{\ell} \ell\]\,,
\\[0.1cm]
  \christoph{\Op_{P(P')}^\ell} &
  = \[\bar{s} P_{R(L)} b\]\!\[\bar{\ell} \gamma_5 \ell\]\,,
\end{aligned}
\end{equation}
and tensor ($i = T,T5$) operators
\begin{equation}
  \label{eq:tensor:ops}
\begin{aligned}
  \christoph{\Op_{T}^\ell} &
  = \[\bar{s} \sigma_{\mu\nu} b\]\!\[\bar{\ell} \sigma^{\mu\nu} \ell\]\,,
\\[0.1cm]
  \christoph{\Op_{T5}^\ell} &
  = \[\bar{s} \sigma_{\mu\nu} b\]\!\[\bar{\ell} \sigma^{\mu\nu} \gamma_5 \ell\]\,,
\end{aligned}
\end{equation}
where the notation $\christoph{\Op_{T5}^\ell} = i/2\, \varepsilon^{\mu\nu\alpha\beta}
\[\bar{s} \sigma_{\mu\nu} b\]\!\[\bar{\ell} \sigma_{\alpha\beta} \ell\]$ is
also used frequently in the literature. The respective short-distance couplings,
the Wilson coefficients $\wilson[(\ell)]{i}(\mu_b)$ are evaluated at a scale of
the order of the $b$-quark mass $\mu_b \sim m_b$ and can be modified from SM
predictions in the presence of new physics.

The SM values $\wilson[(\ell)]{7,9,10}$ are obtained at next-to-next-to leading order
(NNLO) \cite{Bobeth:2003at, Huber:2005ig} and depend on the fundamental parameters
of the top-quark and $W$-boson masses, as well as on the sine of the weak mixing angle.
Moreover, they are universal for the three lepton flavors $\ell = e,\, \mu,\, \tau$.
All other Wilson coefficients are numerically suppressed or zero:
$\wilson[SM]{7'} = m_s/m_b\, \wilson[SM]{7}$, $\wilson[\ell, SM]{S,S',P,P'} \sim
\christoph{m_b m_\ell/m_W^2}$, and $\wilson[\ell, SM]{9',10',T,T5} = 0$.
%Beyond the SM,
%lepton-flavor non-universal effects are possible in principle and have been
%discussed for example recently \cite{Alonso:2014csa, Hiller:2014yaa, Ghosh:2014awa,
%Biswas:2014gga, Hurth:2014vma, Glashow:2014iga, Altmannshofer:2014rta, Hiller:2014abc} in
%connection with the measurement of $R_K = {\cal B}_\mu/{\cal B}_e$ in
%$q^2 \in [1, 6]$ GeV$^2$ \cite{Aaij:2014ora}, which deviates by $2.6\sigma$
%from the SM prediction $R_K^{\rm SM} = 1.00$ \cite{Bobeth:2007dw, Bouchard:2013mia}.
The Wilson coefficients of the four-quark current-current and QCD-penguin
operators as well as of the chromomagnetic dipole operators are set to their
NNLO SM values at $\mu_b = 4.2 \, \mbox{GeV}$ \cite{Bobeth:2003at, Huber:2005ig}.

\christoph{For the rest of this article we will suppress the lepton-flavor index
on the Wilson coefficients: $\wilson[\ell]{i} \to \wilson[]{i}$ and 
operators $\Op_i^\ell \to \Op_i$. In \refsec{sec:results}
we exploit data with $\ell =\mu$ only, hence all derived constraints apply in
principle only to the muonic case, but can be carried over to other lepton
species $\ell = e,\, \tau$ in cases of NP models that do not violate lepton
flavor. In general the Wilson coefficients are decomposed into SM and NP
contributions $\wilson[]{i} = \wilson[SM]{i} + \wilson[NP]{i}$, but often we
will use $\wilson[]{i}$ for Wilson coefficients with zero (or suppressed) SM 
contributions synonymously for $\wilson[NP]{i}$. }

@@

The full dependence of $F_H^\ell$ and $A_{\rm FB}^\ell$ on tensor and scalar
couplings has been presented in \cite{Bobeth:2007dw, Bobeth:2012vn}, adopting
the effective theory \refeq{eq:Heff}, i.e. neglecting higher dimensional operators
with \christoph{$\mbox{dim} \geq 8$}. These results imply that for SM values of the effective
couplings
\begin{align}
  F_H^\ell(q^2) \big|_{\rm SM} & \propto \frac{m_\ell^2}{q^2} 
    \christoph{\bigg/ \Gamma_\ell} \,, &
  A_{\rm FB}^\ell \big|_{\rm SM} & = 0 \,.
\end{align}
Hence, for $\ell = e,\, \mu$ both observables are quasi-null tests. 
The flat term $F_H^\ell(q^2)|_{\rm SM}$ is strongly suppressed \christoph{by small 
lepton masses for the considered kinematical region $1 \leq q^2 \leq 22$ GeV$^2$}
\cite{Bobeth:2007dw, Bobeth:2011nj, Bouchard:2013eph}.  
Nonzero values of $A_{\rm FB}^\ell|_{\rm SM}$ can be induced by higher order QED 
corrections, which will modify the simple $\cos\theta_\ell$ dependence of the angular
distribution~\refeq{eq:ang-distr}, however, currently there is no solid estimate
available for this source of SM background\footnote{The leading QED corrections
  to $B\to X_s\bar\ell\ell$ \cite{Huber:2015sra} might provide an estimate of
  corresponding effects in $B\to K \bar\ell\ell$.}. \todo{David's comment?!}

@@

\begin{table*}
\begin{center}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{lccc}
\hline
Channel & Constraints & Kinematics & Source
\\
\hline \hline
$B_s\to \bar\mu\mu$
& $\int\dd\tau \BR(\tau)$ &  --  & \cite{Aaij:2013aka,Chatrchyan:2013bka,CMS:2014xfa}
\\
\hline
\multirow{5}{*}{${B^+\to K^+ \bar\mu\mu}$}
    & \multirow{2}{*}{$\BR_\mu$}
    & $q^2\in [1,\, 6],\, [14.18,\, 16],\, [> 16]$ GeV$^2$  & \cite{CDF:2012:BKstarll} \\
    &
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014pli} \\
    & $A_{\rm FB}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014tfa, CDF:2012:BKstarll} \\
    & $F_{H}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014tfa} \\
    & $A_{\rm CP}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014bsa}
\\
\hline
    \multirow{3}{*}{${B^0\to K^{\ast 0} \bar\mu\mu}$}
    & $\BR_\mu$
    & $q^2\in [1,\, 6],\, [14.18,\, 16],\, [> 16]$ GeV$^2$  & \cite{CDF:2012:BKstarll, Aaij:2013iag,Chatrchyan:2013cda} \\
    & $A_{\rm FB}^\mu$
    & $q^2\in [1,\, 6],\, [14.18,\, 16],\, [> 16]$ GeV$^2$  & \cite{CDF:2012:BKstarll, Aaij:2013iag,Chatrchyan:2013cda} \\
    & $A_{\rm CP}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014bsa}
\\
\hline
${B\to K}$ form factors
    & $f_{0,+,T}$   &  $q^2 = 17,\, 20,\, 23$ GeV$^2$  & \cite{Bouchard:2013eph} \\
\hline
\multirow{2}{*}{${B\to K^*}$ {form factors}}
    & $V,\,A_{0,1,2},\, T_{1,2,3}$ &  $q^2 = 0.1,\, 4.1,\, 8.1,\, 12.1$ GeV$^2$  & \cite{Straub:2015ica} \\
    & $V,\,A_{0,1,2},\, T_{1,2,3}$
    & $q^2 \in [11.9,\, 17.8]$ GeV$^2$  & \cite{Horgan:2013hoa, Horgan:2015vla}  \\
\hline
\end{tabular}
\renewcommand{\arraystretch}{1.0}
\caption{\label{tab:observables} List of all observables of the various $b\to s
  \bar\mu\mu$ decays entering the fits with the respective kinematics and
  experiments that provide the measurements. LCSR and lattice results of $B\to
  K^{(*)}$ form factors are used to constrain a $q^2$-dependent form-factor
  parametrization.  For more details see \refsec{sec:observables} and
  \refapp{app:theory:inputs}. \checked{} }
\end{center}
\end{table*}

@@

Scalar couplings $\wilson{S,\, S',\, P,\, P'}$ enter $F_H^\ell$ without
kinematic suppression---see \refeq{eq:FH-dependence}---as the sum $(\wilson{i} +
\wilson{i'})$ whereas in the branching ratio $\overline{\cal B}(B_s\to
\bar\ell\ell)$ they appear as the difference $(\wilson{i} - \wilson{i'}), i =
S,\, P$.  Since the existing measurement of $F_H^\mu$ constrains the sum, the
combination of $F_H^\mu$ and $\overline{\cal B}(B_s \to \bar\mu\mu)$ allows
us---for the first time---to bound the real and imaginary parts of all four
couplings.  The corresponding 2D-marginalized regions in the
$\mbox{Re}(\wilson{i} \pm \wilson{i'})$ ($i = S, P$) planes are shown in
\reffig{fig:scalar}. The corresponding plots for $\mbox{Im}(\wilson{i} \pm
\wilson{i'})$ are very similar to those shown and thus omitted. These bounds do
not change when including all other data in \reftab{tab:observables}, since the
$A_{\rm FB}^\mu(B\to K\bar\mu\mu)$ requires interference of scalar with tensor
couplings and other observables are not very sensitive to scalar
couplings. Quantitatively, the constraint from $\overline{\cal B} (B_s \to
\bar\mu\mu)$ on $(\wilson{i} - \wilson{i'})$ is about a factor four to five
stronger than the one of $F_H^\mu$ on $(\wilson{i} + \wilson{i'})$.

@@

\todo{Fred should clarify with Danny on their paper.}
We rescale the observables by the $B^0$-meson life time $\tau_{B^0} =
1.519$~ps~\cite{Agashe:2014kda} to be able to judge if experiments can measure
them in the near future.  At low $q^2$ the posterior predictive ranges are
${\cal O}(10^{-9})$ for $(J_{1s} - 3\, J_{2s})$ and $(J_{1c} + J_{2c})$, getting
suppressed down to ${\cal O}(10^{-10})$ at high $q^2$ due to the
$m_\ell/\sqrt{q^2}$ dependence. In order to compare it to the typical magnitude
of vector couplings, note that for example the branching ratio of $B\to
K^*\bar\ell\ell$
\begin{align}
  \christoph{\BR} &
  = \frac{\tau_{B^0}}{3} \big[
    2\, (3 J_{1s} - J_{2s}) + (3 J_{1c} -  J_{2c})
  \big]
\end{align}
is approximately equal to $2 \cdot 10^{-7}$ in the SM for both the
\christoph{$q^2 \in [1.1,\, 6]$} and $[15,\, 19]$ GeV$^2$ bins.

@@

As a special case, we considered the scenario arising from the SM augmented by
dimension-6 operators generalising existing studies to the case of
complex-valued couplings. In this scenario, tensor couplings are absent and
additional relations between scalar couplings are enforced by the linear
realization of the $SU(2)_L \otimes U(1)_Y$ electroweak symmetry group.

>>>>

\thankstext[$\star$]{t1}{{Preprint: EOS-2015-03,} FLAVOUR(267104)-ERC-107}
\thankstext{e1}{e-mail: frederik.beaujean@lmu.de}
\thankstext{e2}{e-mail: christoph.bobeth@ph.tum.de}
\thankstext{e3}{e-mail: sjahn@mpp.mpg.de}

@@

\begin{abstract}
  The angular distribution of $B\to K\bar\ell\ell$ ($\ell =
  e,\,\mu,\,\tau$) depends on two parameters, the lepton
  forward-backward asymmetry, $A_{\rm FB}^\ell$, and the flat term,
  $F_H^\ell$. Both are strongly suppressed in the standard model and
  constitute sensitive probes of tensor and scalar contributions. We
  use the latest experimental results for $\ell = \mu$ in combination
  with the branching ratio of $B_s\to \bar\mu\mu$ to derive the
  strongest model-independent bounds on tensor and scalar effective
  couplings to date. The measurement of $F_H^\mu$ provides a
  complementary constraint to that of the branching ratio of $B_s\to
  \bar\mu\mu$ and allows us---for the first time---to constrain all
  complex-valued (pseudo-)scalar couplings and their chirality-flipped
  counterparts in one fit. Based on Bayesian fits of various
  scenarios, we find that our bounds even become tighter when vector
  couplings are allowed to deviate from the standard model and that
  specific combinations of angular observables in $B \to K^*$ are
  still allowed to be up to two orders of magnitude larger than in the
  standard model, which would place them in the region of LHCb's
  sensitivity.
\end{abstract}

@@

With the analysis of the data collected by the LHCb Collaboration
during run I at the Large Hadron Collider (LHC), we now have access to
rather large samples of rare $B$-meson decays with branching ratios
below $10^{-5}$. As a consequence, angular analyses of three- and
four-body final states can be used to measure a larger number of
observables than previously possible at the B factories BaBar and
Belle. In this work we focus on rare $B$ decays driven at the parton
level by the flavor-changing neutral-current (FCNC) transition $b\to s
\bar\ell\ell$ that constitutes a valuable probe of the standard model
(SM) and provides constraints on its extensions.

@@

Both {angular} observables, $F_H^\ell$ and $A_{\rm FB}^\ell$, exhibit strong suppression
factors for vector and dipole couplings present in the SM, thereby enhancing
their sensitivity to tensor and scalar couplings \cite{Bobeth:2007dw,
  Bobeth:2012vn}. A similar enhancement of scalar couplings compared to
helicity-suppressed vector couplings of the SM is well-known from $B_s\to
\bar\mu\mu$. Unfortunately the limited data set of $B\to K^*(\to K\pi)
\bar\ell\ell$ from LHCb \cite{Aaij:2013qta} {did not yet} allow to perform a full
angular analysis without the assumption of vanishing scalar and tensor couplings
in this decay mode. In the future with more data or special-purpose analysis
techniques like the method of moments~\cite{beaujean:2015mom}, certain angular
observables in $B\to K^* \bar\ell\ell$ will provide additional constraints on
such couplings, as for example $J_{6c}$ \cite{Altmannshofer:2008dz} and the
linear combinations $(J_{1s} - 3 J_{2s})$ and $(J_{1c} + J_{2c})$
\cite{Matias:2012xw, Bobeth:2012vn} as well as the experimental test of the
relations $H_T^{(2)} = H_T^{(3)}$ and $J_7 = 0$~\cite{Bobeth:2012vn} at low
hadronic recoil.

@@

In the framework of the $|\Delta B| = |\Delta S| = 1$ effective theory
\begin{equation}
  \label{eq:Heff}
\begin{aligned}
  {\cal L}_{\rm eff}  =
   \frac{4 G_F}{\sqrt{2}} \,\frac{\alE}{4 \pi}\, & V_{tb}^{} V_{ts}^\ast
      \, \Big[ {C_7(\mu_b) \Op_7 + C_{7'}(\mu_b) \Op_{7'}}
 \\ & +
       \sum_{\ell = e,\, \mu,\, \tau} \sum_i  \wilson[\ell]{i}(\mu_b)
       {\Op_i^\ell} \Big] + \text{h.c.}
   {\,,}
\end{aligned}
\end{equation}
the most general dimension-six flavor-changing operators {$\Op_i^{(\ell)}$} mediating $b\to
s \gamma$ and $b\to s \bar\ell\ell$ are classified according to their chiral
structure. There are dipole ($i = 7,7'$) and vector ($i = 9,9',10,10'$) operators
\begin{equation}
  \label{eq:SM:ops}
\begin{aligned}
  \Op_{7(7')} &
  = \frac{m_b}{e}\!\[\bar{s} \sigma^{\mu\nu} P_{R(L)} b\] F_{\mu\nu}\,,
\\
  {\Op_{9(9')}^\ell} &
  = \[\bar{s} \gamma_\mu P_{L(R)} b\]\!\[\bar{\ell} \gamma^\mu \ell\]\,,
\\[0.1cm]
  {\Op_{10(10')}^\ell} &
  = \[\bar{s} \gamma_\mu P_{L(R)} b\]\!\[\bar{\ell} \gamma^\mu \gamma_5 \ell\]\,,
\end{aligned}
\end{equation}
further scalar ($i = S,S',P,P'$) operators
\begin{equation}
  \label{eq:scalar:ops}
\begin{aligned}
  {\Op_{S(S')}^\ell} &
  = \[\bar{s} P_{R(L)} b\]\!\[\bar{\ell} \ell\]\,,
\\[0.1cm]
  {\Op_{P(P')}^\ell} &
  = \[\bar{s} P_{R(L)} b\]\!\[\bar{\ell} \gamma_5 \ell\]\,,
\end{aligned}
\end{equation}
and tensor ($i = T,T5$) operators
\begin{equation}
  \label{eq:tensor:ops}
\begin{aligned}
  {\Op_{T}^\ell} &
  = \[\bar{s} \sigma_{\mu\nu} b\]\!\[\bar{\ell} \sigma^{\mu\nu} \ell\]\,,
\\[0.1cm]
  {\Op_{T5}^\ell} &
  = \[\bar{s} \sigma_{\mu\nu} b\]\!\[\bar{\ell} \sigma^{\mu\nu} \gamma_5 \ell\]\,,
\end{aligned}
\end{equation}
where the notation ${\Op_{T5}^\ell} = i/2\, \varepsilon^{\mu\nu\alpha\beta}
\[\bar{s} \sigma_{\mu\nu} b\]\!\[\bar{\ell} \sigma_{\alpha\beta} \ell\]$ is
also used frequently in the literature. The respective short-distance couplings,
the Wilson coefficients $\wilson[(\ell)]{i}(\mu_b)$ are evaluated at a scale of
the order of the $b$-quark mass $\mu_b \sim m_b$ and can be modified from SM
predictions in the presence of new physics.

The SM values $\wilson[(\ell)]{7,9,10}$ are obtained at
next-to-next-to leading order (NNLO) \cite{Bobeth:2003at,
  Huber:2005ig} and depend on the fundamental parameters of the
top-quark and $W$-boson masses, as well as on the sine of the weak
mixing angle.  Moreover, they are universal for the three lepton
flavors $\ell = e,\, \mu,\, \tau$.  All other Wilson coefficients are
numerically suppressed or zero: $\wilson[SM]{7'} = m_s/m_b\,
\wilson[SM]{7}$, $\wilson[\ell, SM]{S,S',P,P'} \sim {m_b
  m_\ell/m_W^2}$, and $\wilson[\ell, SM]{9',10',T,T5} = 0$.  The
Wilson coefficients of the four-quark current-current and QCD-penguin
operators as well as of the chromomagnetic dipole operators are set to
their NNLO SM values at $\mu_b = 4.2 \, \mbox{GeV}$
\cite{Bobeth:2003at, Huber:2005ig}.

For the rest of this article, we will suppress the lepton-flavor index
on the Wilson coefficients $\wilson[\ell]{i} \to \wilson[]{i}$ and
operators $\Op_i^\ell \to \Op_i$. In \refsec{sec:results} we exploit
data with $\ell =\mu$ only, hence all derived constraints apply in
principle only to the muonic case but can be carried over to the other
lepton flavors $\ell = e,\, \tau$ for NP models that do not violate
lepton flavor. In general, the Wilson coefficients are decomposed into
SM and NP contributions $\wilson[]{i} = \wilson[SM]{i} +
\wilson[NP]{i}$ but often we will use $\wilson[]{i}$ for Wilson
coefficients with zero (or suppressed) SM contributions synonymously
with $\wilson[NP]{i}$.

@@

The full dependence of $F_H^\ell$ and $A_{\rm FB}^\ell$ on tensor and
scalar couplings has been presented in \cite{Bobeth:2007dw,
  Bobeth:2012vn}, adopting the effective theory \refeq{eq:Heff},
i.e. neglecting higher-dimensional operators with {$\mbox{dim} \geq
  8$}. These results imply that for SM values of the effective
couplings
\begin{align}
  F_H^\ell(q^2) \big|_{\rm SM} & \propto \frac{m_\ell^2}{q^2}
    {\bigg/ \Gamma_\ell} \,, &
  A_{\rm FB}^\ell \big|_{\rm SM} & = 0 \,.
\end{align}
Hence, for $\ell = e,\, \mu$ both observables are quasi-null tests.
The flat term $F_H^\ell(q^2)|_{\rm SM}$ is strongly suppressed {by small
lepton masses for the considered kinematical region $1 \leq q^2 \leq 22$ GeV$^2$}
\cite{Bobeth:2007dw, Bobeth:2011nj, Bouchard:2013eph}.
Nonzero values of $A_{\rm FB}^\ell|_{\rm SM}$ can be induced by higher-order QED
corrections, which will modify the simple $\cos\theta_\ell$ dependence of the angular
distribution~\refeq{eq:ang-distr}, however, currently there is no solid estimate
available for this source of SM background\footnote{The \christoph{logarithmically
enhanced NLO QED corrections}
  to $B\to X_s\bar\ell\ell$ \cite{Huber:2015sra} might provide an estimate of
  corresponding effects in $B\to K \bar\ell\ell$.}. \todo{David's comment?!}

@@

\begin{table*}
\begin{center}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{lccc}
\hline
Channel & Constraints & Kinematics & Source
\\
\hline \hline
$B_s\to \bar\mu\mu$
& $\overline{\cal B} \equiv \int\dd\tau \BR(\tau)$ &  --  & \cite{Aaij:2013aka,Chatrchyan:2013bka,CMS:2014xfa}
\\
\hline
\multirow{5}{*}{${B^+\to K^+ \bar\mu\mu}$}
    & \multirow{2}{*}{$\BR_\mu$}
    & $q^2\in [1,\, 6],\, [14.18,\, 16],\, [> 16]$ GeV$^2$  & \cite{CDF:2012:BKstarll} \\
    &
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014pli} \\
    & $A_{\rm FB}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014tfa, CDF:2012:BKstarll} \\
    & $F_{H}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014tfa} \\
    & $A_{\rm CP}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014bsa}
\\
\hline
    \multirow{3}{*}{${B^0\to K^{\ast 0} \bar\mu\mu}$}
    & $\BR_\mu$
    & $q^2\in [1,\, 6],\, [14.18,\, 16],\, [> 16]$ GeV$^2$  & \cite{CDF:2012:BKstarll, Aaij:2013iag,Chatrchyan:2013cda} \\
    & $A_{\rm FB}^\mu$
    & $q^2\in [1,\, 6],\, [14.18,\, 16],\, [> 16]$ GeV$^2$  & \cite{CDF:2012:BKstarll, Aaij:2013iag,Chatrchyan:2013cda} \\
    & $A_{\rm CP}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014bsa}
\\
\hline
${B\to K}$ form factors
    & $f_{0,+,T}$   &  $q^2 = 17,\, 20,\, 23$ GeV$^2$  & \cite{Bouchard:2013eph} \\
\hline
\multirow{2}{*}{${B\to K^*}$ {form factors}}
    & $V,\,A_{0,1,2},\, T_{1,2,3}$ &  $q^2 = 0.1,\, 4.1,\, 8.1,\, 12.1$ GeV$^2$  & \cite{Straub:2015ica} \\
    & $V,\,A_{0,1,2},\, T_{1,2,3}$
    & $q^2 \in [11.9,\, 17.8]$ GeV$^2$  & \cite{Horgan:2013hoa, Horgan:2015vla}  \\
\hline
\end{tabular}
\renewcommand{\arraystretch}{1.0}
\caption{\label{tab:observables} List of all observables of the various $b\to s
  \bar\mu\mu$ decays entering the fits with the respective kinematics and
  experiments that provide the measurements. LCSR and lattice results of $B\to
  K^{(*)}$ form factors are used to constrain a $q^2$-dependent form-factor
  parametrization.  For more details see \refsec{sec:observables} and
  \refapp{app:theory:inputs}. \checked{} }
\end{center}
\end{table*}

@@

Scalar couplings $\wilson{S,\, S',\, P,\, P'}$ enter $F_H^\ell$
without kinematic suppression---see \refeq{eq:FH-dependence}---as the
sum $(\wilson{i} + \wilson{i'})$ whereas in the time-integrated
branching ratio $\overline{\cal B}(B_s\to \bar\ell\ell)$ they appear
as the difference $(\wilson{i} - \wilson{i'}), i = S,\, P$.  Since the
existing measurement of $F_H^\mu$ constrains the sum, the combination
of $F_H^\mu$ and $\overline{\cal B}(B_s \to \bar\mu\mu)$ allows
us---for the first time---to bound the real and imaginary parts of all
four couplings.  The corresponding 2D-marginalized regions in the
$\mbox{Re}(\wilson{i} \pm \wilson{i'})$ ($i = S, P$) planes are shown
in \reffig{fig:scalar}. The corresponding plots for
$\mbox{Im}(\wilson{i} \pm \wilson{i'})$ are very similar to those
shown and thus omitted. These bounds do not change when including all
other data in \reftab{tab:observables}, since the $A_{\rm FB}^\mu(B\to
K\bar\mu\mu)$ requires interference of scalar with tensor couplings
and other observables are not very sensitive to scalar
couplings. Quantitatively, the constraint from $\overline{\cal B} (B_s
\to \bar\mu\mu)$ on $(\wilson{i} - \wilson{i'})$ is about a factor
four to five stronger than the one of $F_H^\mu$ on $(\wilson{i} +
\wilson{i'})$.

@@

We rescale $J_i$ and combinations by the $B^0$-meson life time
$\tau_{B^0} = 1.519$~ps~\cite{Agashe:2014kda} to judge the
experimental sensitivity in the near future by comparing to current
measurements of the branching ratio
\begin{align}
  \christoph{\BR} &
  = \frac{\tau_{B^0}}{3} \big[
    2\, (3 J_{1s} - J_{2s}) + (3 J_{1c} -  J_{2c})
  \big] \,.
\end{align}
In the SM, the typical magnitude of the branching ratio of $B\to
K^*\bar\ell\ell$ is approximately equal to $2 \cdot 10^{-7}$ for both
the \christoph{$q^2 \in [1.1,\, 6]$} and $[15,\, 19]$ GeV$^2$
bins. For comparison, the predicted ranges for $\tau_{B^0}(J_{1s} -
3\, J_{2s})$ and $\tau_{B^0}(J_{1c} + J_{2c})$ in the SM are
suppressed by $2-3$ orders of magnitude down to ${\cal O}(10^{-10})$;
cf. \reftab{tab:postdictions}.

@@

As a special case, we consider the scenario arising from the SM
augmented by dimension-6 operators generalizing existing studies to
the case of complex-valued couplings. In this scenario, tensor
couplings are absent and additional relations between scalar couplings
are enforced by the linear realization of the $SU(2)_L \otimes U(1)_Y$
electroweak symmetry group.
